Hypertension and microbiome

### 2019-01-03 rrbiome.Rmd
Full re run for adonis

calculateadonis <- function(dset,
                            matrix,
                            responses = list(model_1 = "MAP", model_2 = "SYSTM", model_3 = "DIASM",
                                          model_4 = "PULSEPRESSURE", model_5 = "HYPERTENSION"),
                            covariates = c("BL_AGE", "SEX"),
                            npermutations = 99,
                            maxcores = 100) {
    mclapply(responses, function(response) {
        fo <- paste(response, covariates, sep = " + ", collapse = " + ")
        ad <- adonis(as.formula(paste(matrix, fo, sep = "~")), data = dset, permutations = npermutations)
        ad$aov.tab %>%
            as.data.frame %>%
            tibble::rownames_to_column(var = "term") %>%
            dplyr::mutate(response = response)
      }, mc.cores = min(maxcores, length(responses)))
}

>>>>

calculateadonis <- function(dset,
                            matrix,
                            responses = list(model_1 = "MAP", model_2 = "SYSTM", model_3 = "DIASM",
                                          model_4 = "PULSEPRESSURE", model_5 = "HYPERTENSION"),
                            covariates = c("BL_AGE", "SEX"),
                            npermutations = 99,
                            maxcores = 100) {
    mclapply(responses, function(response) {
	fo <- sprintf("matrix ~ %s + %s", response, paste(covariates, collapse = " + "))
        ad <- adonis(as.formula(fo), data = dset, permutations = npermutations)
        ad$aov.tab %>%
            as.data.frame %>%
            tibble::rownames_to_column(var = "term") %>%
            dplyr::mutate(response = response)
      }, mc.cores = min(maxcores, length(responses)))
}
